Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-07 analysis/paper/paper.qmd
refactor table 2 code

format_percent <- scales::label_percent(0.1)

predator_context <- tribble(
  ~species, ~`Typical prey`, ~`Foraging behavior`,     ~Reference,
  "SNPT",   "Myctophids",    "Surface feeding (<5 m)", "@spearMorphologicalDifferencesRelative1998; @delordSpeciesSpecificForaging2016",
  "ANPT",   "Myctophids, krill, squid",    "Surface feeding (<5 m)", "@spearMorphologicalDifferencesRelative1998; @delordAntarcticPetrelsIce2020",
  "SGPT",   "Juvenile pinnipeds and seabirds, carrion",    "Scavenging, surface feeding (<5 m)", "@hunterFoodFeedingEcology1983",
  "FUSE",   "Krill, myctophids",    "Diving (~15-50 m)", "@stanilandForagingBehaviourTwo2011",
  "KEGU",   "Limpets, krill",    "Surface feeding (<5 m)", "@silvaDoesAccessHighquality2001",
  "ANFU",   "Myctophids, krill, squid",    "Surface feeding (<5 m)", "@ridoux1989diets; @spearMorphologicalDifferencesRelative1998",
  "CAPT",   "Krill, myctophids",    "Surface feeding (<5 m)", "@ridoux1989diets; @spearMorphologicalDifferencesRelative1998",
  "ADPN",   "Krill",    "Diving (~15-50 m)", "@ciminoClimatedrivenSympatryMay2016; @juaresDietAdeliePenguins2018",
  "CRSE",   "Krill",    "Diving (~50-100 m)", "@burnsWinterHabitatUse2004; @huckstadtDietSpecialistChanging2012",
  "BLPT",   "Krill, myctophids, amphipods",    "Surface feeding (<5 m)", "@princeFoodFeedingEcology1980",
  "LESE",   "Seals, penguins, fish, rkill",    "Diving (~50-100 m)", "@walkerSeasonalOccurrenceDiet1998; @casauxDietLeopardSeal2009; @krauseNovelForagingStrategies2015",
  "ANTE",   "Krill, myctophids",    "Surface feeding (<5 m)", "@croxallFoodFeedingEcology1980; @ainley1992does",
  "PFSB",   "Carrion",    "Scavenging", "@faveroForagingEcologyPaleFaced1996",
  "MIWH",   "Krill",    "Diving (~5-100 m)", "@friedlaenderFeedingRatesUnderice2014",
  "WESE",   "Fish, squid",    "Diving (~100-350 m)", "@testaOverwinterMovementsDiving1994; @lakeRegionalTemporalFinescale2003",
  "GEPN",   "Krill, fish",    "Diving (~25-100 m)", "@croxallFoodFeedingEcology1980; @ciminoClimatedrivenSympatryMay2016",
  "ELSE",   "Myctophids, squid",    "Diving (~200-800 m)", "@guinetSouthernElephantSeal2014; @daneriFeedingHabitsSouthern2015",
  "KIWH",   "Whales, seals, toothfish, penguins",    "Complex and diverse", "@pitmanThreeFormsKiller2003",
  "EMPN",   "Krill, silverfish",    "Diving (~50-300 m)", "@kirkwoodForagingEcologyFemale1997; @rodaryBenthicDivingMale2000",
  "SBWH",   "Squid",    "Diving (>500 m)", "@macleodReviewDataDiets2003",
  "ANSH",   "Demersal fish",    "Diving (<50 m)", "@casauxShagsAntarcticaTheir2006",
  "ROSE",   "Myctophids, squid",    "Diving (~100-300 m)", "@blixRossSealOmmatophoca2007; @southwellReviewDataAbundance2012"
)

n_sites <- nrow(read_obj("zoop_sf"))

read_obj("predators_stations") %>% 
  mutate(common = code_to_common(species),
         scientific = code_to_scientific(species),
         Species = str_glue("{common} _{scientific}_")) %>% 
  group_by(Species, species) %>% 
  summarize(Ind = sum(count),
            Sites = n(),
            `Freq (%)` = format_percent(Sites / n_sites[1]),
            .groups = "drop") %>% 
  left_join(predator_context, by = "species") %>% 
  select(-species) %>% 
  arrange(desc(Sites)) %>% 
  knitr::kable()

>>>>

make_predatortbl(read_obj("predators_stations"), read_obj("zoop_sf"))
